---
title: "hw1_app_stat"
output: pdf_document
author: Kvan Valerii
date: '2022-03-23'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```

$$
 y = 2|x| - \pi, x \in [-{pi\over2},{pi\over2}], y >= -\pi
$$
$$
 y = |sin(2x)|, x \in [-{pi\over 2},{pi\over 2}], y \in [0, 1]
$$
Range for x and y in total:

$$
 x \in [-{pi\over 2},{pi\over 2}], y \in [-\pi, 1]
$$

# Generate points 

Use uniform distribution to generate points between y and x range separately

```{r cars}
numTrials = 100000
x = runif(numTrials, min = -pi/2, max = pi/2)
y = runif(numTrials, min = -pi, max = 1)
points <- data.frame(
  x,
  y)


inFunctionArea <- y >= 2*x-pi & y >= -2*x-pi &
  y <= sqrt(sin(2*x)^2) 

```

## Plot of generated points

Blue points are inside area defined by functions
Red are not inside this area

```{r pressure}
ggplot(points) +
  geom_point(aes(x = x, y = y, color = inFunctionArea), size = 0.7) +
  theme_minimal()
```
To calculate blue we can use next formula:

$$
S_{approx} = \frac{n_{inside} * S_{rectangle}}{n_{total}}
$$
where 
 $S_{rectangle}$ - is area of rectangle (from -pi to 1 on y and from -pi/2 to pi/2 on x) 
 
 $S_{approx}$ - is approximated blue area
 
 $n_{inside}$ - is count of generated points that is inside blue area
 
 $n_{total}$ - is total count of generated points

This is result

```{r}
ratio <- sum(inFunctionArea) / numTrials
area_rect <- (1 + pi) * (pi/2 + pi/2)
area = ratio * area_rect 
area
```

